### 2012-07-04 inst/examples/Reed.Rmd
Reed compared to clark

``` {r policyfn_plot}
require(reshape2)
policies <- melt(data.frame(tsock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")

q1 <- ggplot(policies, aes(x_grid, x_grid - value)) + geom_point() + geom_line() + xlab("stock size") + ylab=("escapement") 
q1
````

>>>>

``` {r policyfn_plot}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")

q1 <- ggplot(policies, aes(x_grid, x_grid - value, color=variable)) + geom_point() + geom_line() + xlab("stock size") + ylab=("escapement") 
q1
````
